---
title: "dfdr — automatic differentiation of simple functions in R"
author: "Thomas Mailund"
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/mailund/dfdr.svg?branch=master)](https://travis-ci.org/mailund/dfdr)
[![Coverage Status](https://img.shields.io/codecov/c/github/mailund/dfdr/master.svg)](https://codecov.io/github/mailund/dfdr?branch=master)


# dfdr — Automatic differentiation of simple functions in R

The `dfdr` package implements a simple version of automatic differentiation. It takes functions that consist of a single expression and construct the derivative with respect to a specific variable. 

To install `dfdr` you can use `devtools`.

```r
install.packages("devtools")
devtools::install_github("mailund/dfdr")
```

and then load the library with

```{r}
library(dfdr)
```

To compute the derivative of a function, you use the function `d`. It takes two arguments, the function to compute the derivative of and the variable to compute the derivative with respect to.

```{r}
f <- function(x) x^2
df <- d(f, "x")
df
```

The body of the deriatives are not simplified right now, so they tend to be more complex than you would normally see them. When computing the derivative, `d` simply follows simple rules for computing the derivatives of expressions and handles complex expressions using the chain rule. I plan to add partial evaluation to the function later to simplify expressions.

Currently, it just handles arithmetic expressions, but I will implement handling of functions in the expressions as well, soon.
